### 2014-02-19 Draft/abstract.tex
Updated some  reading group comments

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequences of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal temporal specifications from natural language text of API documents.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

% need to explain why moving from formal specifications to temporal constraints

% Goal statement
% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints etc.. 
\end{abstract}

>>>>

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequences of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal temporal specifications from natural language text of API documents.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 70\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

% Goal Statement
% Negating everything as we go along
% Instead of despite 
% need to explain why moving from formal specifications to temporal constraints
% bridging
% Goal statement
% The goal of this research is to facilitate the correct usage API methods by identifying temporal constraints.
% to support tool based verfication
% Avoid starting the abstarct with a definition
% bridge the gap
% There is an order that API documents tell 
% but they are 
% Adhering to temporal constraints is mandatory for correct usage of API
% However, it not starightforward to 
% Motivation
% Goal
% Evaluation
% Structured Abstract
% what is the significance of this prescison i/p o/p
% expresses 
% makes end to end summary.

% where do you loose precision and recall.
\end{abstract}

### 2014-02-19 Draft/approach.tex
Updated some  reading group comments

The preprocessor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation. The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.

We next describe each component in detail.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approachs.
In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence.
We define our representation as a tree structure that is essentially a First-Order-Logic (FOL) expression.
Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
All of these semantic templates are publicly available on our project website~\cite{projectweb}.
With respect to the previous example the template no. 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\begin{enumerate}
	\item The sentence is not from parameter summary or return variable summary.
	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
	\item The sentences contains modal modifiers such as ``can, could, may, must, should'' expressing necessity.
	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``if''.
\end{enumerate}

>>>>

The preprocessor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation. The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
We next describe each component in detail.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approachs.
In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

The text analysis engine component accepts the annotated documents and creates an intermediate representation of each sentence.
We define our representation as a tree structure that is essentially a FOL expression.
Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
All of these semantic templates are publicly available on our project website~\cite{projectweb}.
With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\begin{enumerate}
	\item The sentence is not from parameter summary or return variable summary.
	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}''.
\end{enumerate}

### 2014-02-19 Draft/background.tex
Updated some  reading group comments

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: ''Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

>>>>

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

### 2014-02-19 Draft/example.tex
Updated some  reading group comments

We now present some real world examples to motivate our approach. In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation. We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
pages. For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages. Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that do not follow temporal specifications. 
If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{Stackoverflow.eps}
\end{center}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}. Stack Overflow is a question and answer site for professional and enthusiast programmers. The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI. In particular, the query complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}. In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon. Figure~\ref{fig:AmzonS3DeleteBucketAPI} shows the documentation of delete bucket method. The documents states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted. Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction. In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
\end{center}
\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
\end{figure}

Formal verification tools can be used to find such kind of defects. However, formal analysis
tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal machine understandable form. 
Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{Example2.eps}
\end{center}
\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
\end{figure}

>>>>

We now present some real world examples to motivate our approach. In particular, through these examples, we demonstrate that developers often ignore the tempral specifications of an API present in its documentation. We suspect the reason for this phenomena is that API documentation is often verbose and information is distributed across various
pages. For example, the PDF version of the documentation for Amazon S3 API\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages. Developers do not have time and patience to go through all the documentation and miss various temporal specifications of the API, resulting in defective applications that invoke API methods in sequences prohibited by documentation. 
If we have the formal temporal specifications such kinds of defects can be detected by formal verification tools.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.45]{Stackoverflow.eps}
\end{center}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is a question and answer site for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon.
The document clearly states that before deleting the bucket, the objects in the buckets must be deleted. \textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but notice that one of the responses on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.
In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}, \textit{(``...paying for excess stuff you don't need is simply idiotic...'')}.

%\begin{figure}[t]
%\begin{center}
%\includegraphics[scale=0.5]{AmzonS3DeleteBucketAPI.eps}
%\end{center}
%\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
%\end{figure}

Formal verification tools can be used to easily find such kind of defects.
However, formal analysis tools are not designed to work on specifications in natural languages (such as API Documents) and require the specifications in a more formal or machine understandable format. 
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation. In next section, we briefly discuss the related work in this area.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{Example2.eps}
\end{center}
\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
\end{figure}

### 2014-02-19 Draft/introduction.tex
Updated some  reading group comments

Despite being desirable, most API's do not have formal specifications.
In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
Typically, an API document describes both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the current method.
We observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations describe temporal constraints.
Although API documents contain temporal constraints in natural language, formal analysis tools are not designed to work on specifications written in natural languages.

One way of addressing the issue, is to manually convert the natural language API description into formal specifications. 
However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.

%Strike out ``To address the aforementioned issue''
We propose a novel approach to infer temporal usage constraints from natural language text of API documents. We propose a new approach that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer temporal usage constraints. 
%In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
There are existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}. 
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods. Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.

First, relying just on type information will result in a incomplete list of temporal constraints. 
Although, in typed languages some temporal constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints with the the constraints inferred from
the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentence stating that we extend previous technique to address the issues 
Second, inferring temporal constraints from the natural language text itself is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
Recall, the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances require domain dictionaries.
Ad-hoc constructing these dictionaries is prohibitively time and resources intensive.
To address this challenge, we propose to build domain-dictionaries systematically from API documents themselves.

@@

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item A NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
	\item An evaluation of proposed approach on 
commonly used package \CodeIn{java.io} from JDK API and Amazon
S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
an average of 60\% precision and 80\% recall in inferring 63
temporal constraints from more than 2400 sentences of API
documents.
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents an real world examples that motivate our approach.
Section~\ref{sec:related} discusses related work in this area.
Section~\ref{sec:background} presents the  background on code contracts as well as NLP.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents evaluation of our approach.
Section~\ref{sec:discussion} presents a brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.

>>>>

Despite being desirable, most API's do not have formal specifications.
In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
We observed that roughly 12\% of the sentences (that describe some sort of specification constraints) in \amazonAPI\ documentations describe temporal constraints.
Although API documents contain temporal constraints, existing formal analysis tools are not designed to work on specifications written in natural language.

One way of addressing the issue, is to manually convert the natural language API description into formal specifications. 
However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web service API, even before they attempted to formalize the constraints on the method.

%Strike out ``To address the aforementioned issue''
%We propose a novel approach to infer temporal usage constraints from natural language text of API documents. 
In contrast to manual approach, we propose an automated approach that applies Natural Language Processing (NLP) techniques on natural language text in API documents to infer temporal usage constraints. 
%In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
\textbf{There are} existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}. 
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods. Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.

First, relying just on type information will result in an incomplete list of temporal constraints. 
In typed languages some temporal constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from
the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentence stating that we extend previous technique to address the issues 
Second, inferring temporal constraints from the natural language text itself is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
Recall the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively time and resources intensive.
To address this challenge, we propose to build domain-dictionaries systematically from API documents and generic English dictionaries.

@@

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
	\item An evaluation of proposed approach on 
commonly used package \CodeIn{java.io} from JDK API and Amazon
S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
an average of 70\% precision and 80\% recall in inferring 63
temporal constraints from more than 2400 sentences of API
documents.
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents real world examples that motivate our approach.
Section~\ref{sec:related} discusses related work in this area.
Section~\ref{sec:background} presents the  background on NLP techniques used in this work.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents evaluation of our approach.
Section~\ref{sec:discussion} presents a brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.
